\documentclass[12pt,a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listings}

\title{Graph Powered Machine Learning - Exercise 2}
\author{J{\"o}rg Schad}

\begin{document}
\maketitle

Thank you for participating in the Graph Powered Machine Learning Workshop! This is the second of two Exercises.

\section*{Logistics}

\begin{itemize}
  \item You can submit into groups up-to 4 people, please include: 
  \begin{itemize}
  \item Full Name
  \item Student ID and Affiliation
  \item Email Address
  \end{itemize} for all group members
  \item Deadline: October 2nd, 23:59 CET
  \item Submit to joerg@arangodb.com
  \item Code can be either submitted in .py file or as .ipynb notebook (will give you the chance to add additional information)
  \item Feel free to use existing notebooks as starting point

\end{itemize}


\section{A Comprehensive Survey on Graph Neural
Networks}

Read sections 1,2,3,6 of the \href{https://arxiv.org/pdf/1901.00596v1.pdf}{A Comprehensive Survey on Graph Neural
Networks} and discuss the following questions (roughly 1-2 paragraphs each):
\begin{enumerate}
    \item How are network embeddings and GCNs related?
    \item What are the potential outputs of GCNs? Please describe one use-case for each potential output. 
    \item What are value is added by Graph Attention Networks over GCNs? What are potential disadvantage? 
    \item Why are GCNs relevant for Computer Vision?
\end{enumerate}


Note: Just in case you want to read more even after the completing the remaining sections in the above paper \href{https://arxiv.org/abs/1812.08434}{Graph neural networks: a review of methods and applications} is good addition.

\section{Graph Learning Tasks}
Pick one of the following Graph Learning Tasks from the \href{https://docs.dgl.ai/guide/training.html}{DGL Guide} and create a python tutorial (preferably as jupyter  notebook) for that example. Feel free to choose another dataset (http://kaggle.com is a good starting point). 
\begin{enumerate}
   \item Node Classification/Regression
\item Edge Classification/Regression
\item Link Prediction
\item Graph Classification
\end{enumerate}



\end{document}